Sparse Representation Approaches for First Stage Retrieval: A Review

### 2021-11-28 src/article.tex
Update section [Problem formalization]
Each sentence on new line
Update section [Problem formalization]. Update and refactoring bibliography.

>>>>

    Ideally, the goal of the first stage of a search is to retrieve all relevant documents from the
    collection.
    In this regard, when building a model, it is necessary to strive to ensure that it can return
    the most complete set of relevant documents in a short period of time.

    For a long time, term-based models were used for the first stage of search, which showed high
    efficiency due to simple logic and the use of an inverse index
    \cite{termBasedModelEfficiency1, termBasedModelEfficiency2}.
